### 2023-11-07 main.tex
^^

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
% MACROS
% % 
% \newcommand{\cristian}[1]{{\bf (* {\color{ForestGreen}V:{} \small #1}*)}}
% \newcommand{\jorge}[1]{{\bf (* {\color{BlueViolet}G:{} \small #1}*)}}
% \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}

\frenchspacing

@@

\vspace{.5cm}
\noindent
{\bf Remark.} In the following we will often consider type $N$ as a distinguished type
(called `holes'), whose number at each site is fixed by the numbers of particles 
of the remaining $N-1$ types. It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
(those of types $\{1,\ldots,N-1\}$), we retrieve the 
boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
The choice of type $N$ for the distinguished type is arbitrary and does not affect
the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
the dual process eventually has only particles of type $N$ on the graph.
Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.

@@

 In this context, it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by

@@

\newline
\newline
\textbf{Remark}:

@@

@@

We define the duality function of the open multi-species stirring process as
\begin{equation}\label{dualityElements}
	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
\end{equation}
where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
\begin{equation}
\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
\end{equation}
The dual process is defined by its Markov generator, which reads
 \begin{equation}\label{DualGenerator}
    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
\end{equation}
where 
$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
\begin{equation}\label{siteDualGenerator}
    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)\dt
\end{equation}
\newline
Therefore the dual dynamics is described as follows. On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multi-species stirring dynamics on the graph. On the other hand, the site
part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{1,\ldots,N-1\}$ at site $x$ with a particle of type $N$ and creates a particle of the same type $a$ at the extra-site $u(x)$. This last transition is performed with rate $|\alpha^{x}|\xi_{a}^{x}$. This means that eventually the dual process voids the graph, putting all the dual particles of species $\{1,\ldots,N-1\}$ in the extra-sites. In other words the extra-sites play the role of absorbing boundaries. 
\newline \newline
\textbf{Remark}: in the reversible situation, i.e. when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
\begin{equation}
\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt
\end{equation}

\subsection{Proof of duality}
To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.  To show this, we will use the Hamiltonians and their Lie algebraic description. Indeed, in this formalism the proof 
reduces to finding symmetries of the generator (for the bulk duality) and group like transformations (for the ``boundary duality'').

@@

\newline \newline
\textbf{Remark}: Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.

@@

 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \\ \\The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of exact correlations are in general involving. 

@@

\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.

@@

\subsection{Proof of th exact correlations in the non-equilibrium steady state}
[ADD TEXT]

@@

\textbf{Remark:} The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e. to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}. They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp. $(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp. $\beta_a$).
\newline\newline

@@

\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP. \\ \\
\textbf{Remark:}  

@@

with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have

@@

The computations made for the multi-species stirring process can be specialized for the colour-blind case, i.e. the situation in which only one type of non-empty particle is considered. In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations. 

@@

\begin{equation}\label{steadyStateH}
 Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression. We report the explicit formula and the proof in Appendix \ref{appB}.\\
In \eqref{SteadyState-coeff-implicit} there are two terms. For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}. The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$ computed in these new configurations with proper coefficients. If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.\\
The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}. If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
 For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
where $x_{k}$ is the position of the $k$-th particle among $q$. 
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, thus we have that 
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
Moreover, we observe that 
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
All in all we obtain 
\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
\subsubsection{Exact steady state correlations}

\begin{comment}
 introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
\begin{align}
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{align}
We observe that, at most $q$ factors do survive in the product over $k$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
\begin{equation}
	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{equation}
We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
\begin{equation}
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
\end{equation}
Moreover, we observe that 
\begin{equation}
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
\end{equation}
All in all we have that
\end{comment}

@@

@@

		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}

@@

	By introducing the notation \eqref{eta-notation} and by considering 

@@

				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})

@@

		Using \eqref{elementsABS} we have 
				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}

>>>>

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
% MACROS
% % 
% \newcommand{\cristian}[1]{{\bf (* {\color{ForestGreen}V:{} \small #1}*)}}
% \newcommand{\jorge}[1]{{\bf (* {\color{BlueViolet}G:{} \small #1}*)}}
% \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}
 \newtheorem{remark}{Remark}
\frenchspacing

@@

\vspace{.5cm}
\noindent
\begin{remark}
In the following we will often consider type $N$ as a distinguished type
(called `holes'), whose number at each site is fixed by the numbers of particles 
of the remaining $N-1$ types. It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
(those of types $\{1,\ldots,N-1\}$), we retrieve the 
boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
The choice of type $N$ for the distinguished type is arbitrary and does not affect
the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
the dual process eventually has only particles of type $N$ on the graph.
Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.  
\end{remark}

@@

 In this context it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by

@@

\begin{remark}

@@

\end{remark}

@@

We define the duality function of the open multi-species stirring process as
\begin{equation}\label{dualityElements}
	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
\end{equation}
where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
\begin{equation}
\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
\end{equation}
The dual process is defined by its Markov generator, which reads
 \begin{equation}\label{DualGenerator}
    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
\end{equation}
where 
$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
\begin{equation}\label{siteDualGenerator}
    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)\dt
\end{equation}
\newline
Therefore the dual dynamics is described as follows. On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multi-species stirring dynamics on the graph. On the other hand, the site
part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{1,\ldots,N-1\}$ at site $x$ with a particle of type $N$ and creates a particle of the same type $a$ at the extra-site $u(x)$. This last transition is performed with rate $|\alpha^{x}|\xi_{a}^{x}$. This means that eventually the dual process voids the graph, putting all the dual particles of species $\{1,\ldots,N-1\}$ in the extra-sites. In other words the extra-sites play the role of absorbing boundaries. 
\newline \newline
\begin{remark} in the reversible situation, i.e. when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
\begin{equation}
\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt
\end{equation}
\end{remark}
\subsection{Proof of duality}
To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.  To show this, we will use the Hamiltonians and their Lie algebraic description. Indeed, in this formalism the proof 
reduces to finding symmetries of the generator (for the bulk duality) and group like transformations (for the ``boundary duality'').

@@

\begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.

@@

 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of exact correlations are in general involving. 

@@

\begin{remark} the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
	\end{remark}

@@

\subsection{Proof of the exact correlations in the non-equilibrium steady state}
The proof of formula \eqref{exactCorrelations} is made in some steps:
\begin{itemize}
	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular diagonal boundaries respectively. Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 
	\item In Subsection \ref{subsectionSSHsec} we apply the MPA to $H^{''}$. Here the commutation relations defining the matrix algebra are simpler. The explicit expression for $|\Psi^{''}\rangle$ is determined (see \eqref{ResulsBasis}).
	\item In subsection \ref{subsectionSSdual}, we invert one of the similarity transformation recovering the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$ computed in the previous step (see \eqref{ABS}).
	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step. Using duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report it Appendix \ref{appB}. 
\end{itemize}

@@

\begin{remark}
	The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e. to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}. They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp. $(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp. $\beta_a$).
\end{remark}

@@

\begin{remark} By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

This formula will be useful in the following. 
\end{remark}

@@

with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$. Thus we have

@@

The computations made for the multi-species stirring process can be specialized for the colour-blind case $N=2$, i.e. when only one type of non-empty particle is considered. In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations. 

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$

 Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression. We report the explicit formula and the proof in Appendix \ref{appB}.\\
\\
The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
\end{comment}
\begin{comment}
\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}. If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
\begin{align}
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
\end{align}
 For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
\begin{equation}
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
\end{equation}
where $x_{k}$ is the position of the $k$-th particle among $q$. 
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, thus we have that 
\begin{equation}
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
\end{equation}
Moreover, we observe that 
\begin{equation}
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
\end{equation}
All in all we obtain 
\begin{equation}\label{PsiI-N2}
\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
\end{equation}
\end{comment}

\begin{comment}
	\subsubsection{Exact steady state correlations}
 introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
\begin{align}
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{align}
We observe that, at most $q$ factors do survive in the product over $k$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
\begin{equation}
	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
\end{equation}
We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
\begin{equation}
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
\end{equation}
Moreover, we observe that 
\begin{equation}
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
\end{equation}
All in all we have that

@@

In \eqref{SteadyState-coeff-implicit} there are two terms. For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}. The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$. If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
\begin{remark}
	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
As a consequence, one cha interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$. 
\end{remark}
\begin{remark}
The coefficients $\Psi(\bm{\tau})$ can also be written explicitly by replacing $\Psi^{'}(\bm{\tau})$ with formula \eqref{ABS}. They read 

@@

@@

	Considering 

@@

				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})

@@

		%Using \eqref{elementsABS} we have 
		%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
